---
title: "Discount - Sales Analysis"
author: "Merly Varghese"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: cerulean
    highlight: tango
---

```{r setup, include=FALSE}
library(prettydoc)
knitr::opts_chunk$set(echo = TRUE)
```

&nbsp;

## What is  linear regression ?

Linear regression is a commonly used technique in predictive analytics, which build a model to explain the change in one variable based on the linear relationship with other variables. 
Linear Regression can be classified as follows:

*  __*Simple Linear Regression*__ :  A single variable can explain the change in the dependent variable.
*  __*Multiple Linear Regression*__ :  Change in the dependent variable can be explained by multiple variables.

## About Data

Data used for this analysis is the dummy data generated for sales of different category of items in an outlet. The column names are described below

*  __*UPC*__  : Unique Product Code of the item
*  __*Category*__  : Category name. The categories included in the data are
Vegetable & fruits, meat & fish , snacks, diary and Care products.
*  __*Price*__  : Price per unit of the item ( INR)
*  __*Discount*__  : Discount applied for the item.(%)
*  __*Sales*__  : Total sales recorded for the item after the discount applied (INR)

## Objective

Analyze how percentage of discount influence the product sales in different categories and predict sales using the data provided 


## Data exploration

In the data, all categories have around 80 unique items and the plot given below explains the combined sales of products across all categories.

&nbsp;

```{r load_library, echo=FALSE,warning=FALSE,include=FALSE}
library(openxlsx)
library(data.table)
library(dplyr)
library(ggplot2)

```

```{r source_code, echo=FALSE,warning=FALSE,include=FALSE}

source("../R/functions.R")
```

```{r read_data, echo=FALSE,warning=FALSE,fig.width=5,fig.height=3}
#Read data
sales_data <- read.xlsx("../Data/Sales_Data.xlsx")
sales_data <- sales_data %>% data.table()
#aggregate  data  and find total sale in each category
sales_data_agg <- sales_data %>% .[,.(TotalSales =sum(Sales)
                                                      ,UpcCount = .N)
                                                      ,by = (Category)]
#Visualize the total sales
plot1 <- ggplot(data = sales_data_agg
       ,aes(x =Category,y= TotalSales,fill =Category ))+
        geom_bar(stat = "identity",width = .5,) +
        theme(panel.grid.major = element_blank()
              , panel.grid.minor = element_blank()
              , panel.background = element_blank()
              , axis.line = element_line(colour = "black")
              , legend.position="none"
              ) +
          ggtitle("Total Sales :  Category")

plot1 + coord_flip() #for horizontal alignment

```


&nbsp;

The major part of the sales is made by food products such as Vegetable & Fruits and Meat &fish. Items under the category care products has comparatively less sales among all the categories.

## Category Wise Analysis{.tabset}


```{r models, echo=FALSE,warning=FALSE,fig.width=5,fig.height=3}

snack_model <- get_model(sales_data,"SNACKS")
veg_model <-  get_model(sales_data,"VEGETABLE&FRUITS")
meat_model <- get_model(sales_data,"MEAT&FISH")
care_model <-  get_model(sales_data,"CARE PRODUCTS")
diary_model <- get_model(sales_data,"DIARY")
```

### VEGETABLE&FRUITS




Linear model equation :

$$ Sales = `r round(veg_model[[2]])` * Price + `r veg_model[[3]]` * Discount + `r veg_model[[1]]`$$

$$Adjusted R-squre  = `r round(veg_model[[4]])`$$
**Conclusion** :

Discount has a positive correlation with the sales.ie, as Discount increases, a similar increasing trend visible in sales.


### SNACKS

Linear model equation :

$$ Sales = `r round(snack_model[[2]])` * Price + `r snack_model[[3]]` * Discount + `r snack_model[[1]]`$$

$$Adjusted Rsqure  = `r round(snack_model[[4]])`$$

### MEAT&FISH

Linear model equation :

$$ Sales = `r round(meat_model[[2]])` * Price + `r meat_model[[3]]` * Discount + `r meat_model[[1]]`$$

$$Adjusted Rsqure  = `r round(meat_model[[4]])`$$

### CARE PRODUCTS

Linear model equation :

$$ Sales = `r round(care_model[[2]])` * Price + `r care_model[[3]]` * Discount + `r care_model[[1]]`$$

$$Adjusted Rsqure  = `r round(care_model[[4]])`$$


### DIARY


Linear model equation :

$$ Sales = `r round(diary_model[[2]])` * Price + `r diary_model[[3]]` * Discount + `r diary_model[[1]]`$$

$$Adjusted Rsqure  = `r round(diary_model[[4]])`$$

